\chapter{Conclusion}\label{ch:concl}
	\section{Idea}
	At the start we decided to reformat a well known classic game. Mazes are good time-killer, rules are easy and difficulty is amusing. To add some competitiveness, we added a possibility to play with a friend.
	\section{Implementation}
	\subsection{Design}
	For now, we brought an amazing design, which makes our application look friendly and interesting. UX is also user-friendly, right after user loads main page he can see "PLAY" button and that's all what he needs from this page, also it contains some information about project. 
	\subsection{Backend}
	For the backend we did a big work on making mazes look natural and interesting enough to keep user's focus. Implementation based on algorithms and data structures. In the relevant chapter we added all details on optimization and some math calculations.
	\subsection{Frontend}
	Frontend is a quintessence of our work, because it is where our design meets technical part. Using some techniques and approaches to make playing easy and comfortable, we built a user-friendly game for wide auditory.
	
	\section{Problems}
	As any team, we faced some problems and failed to implement some of thing for this stage. Firstly, it is lack of resources. We can't get high-performance hardware and software for free, so it is the place we met problems. Any online communication with a high tempo should be done with a high stability and accurate approach. So, for now, we decided to make some things easier and leave place for future expansion.